Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-26 document/ms.tex
generalities

%
%  RULES OF THE GAME, MOTHAFUCKERS.
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * that is all.
%

@@

\section{The model}

>>>>

%
%  RULES OF THE GAME, MOTHAFUCKERS.
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ALWAYS cite inside parens () and use \citealt{}; no in-line cites
%  * that is all.
%

@@

\section{Model generalities}

From our perspective, a ``model'' is a likelihood function---a probability
density (or distribution) function (PDF) for the data given
parameteters---and a set of prior PDFs for the parameters.
In what follows, we will treat as ``data'' a certain set of exoplanet radius
and period measurements (\citealt{petigura}).
We will treat the uncertainties on those measurements as ``prior
information''; that is, we will treat those as true as given and not as being
generated by the parameterized likelihood function.

In the models that follow, the most important parameters will be parameters
of the PDF for the exoplanet radii and periods.
However, there will also be ``latent parameters'' that represent the ``true''
values of the exoplanet radii and periods.
That is, for each exoplanet, there is a ``measured'' or ``observed'' radius
and period, which constitute our data.
These relate to the unobserved ``true'' radius and period by a noise model.
For the conclusions of this study, the true values of radius and period are
nuisance parameters; we will marginalize them out.
